---
title: "do_temp_synth"
output: html_document
date: "2026-01-21"
---

Do this after you've gotten maxmin dfs for temp and DO 

## Load libraries
```{r}
library(tidyverse)
library(glmmTMB)
library(DHARMa)
library(readr)
library(ggplot2)
library(readxl)
library(lubridate)
library(purrr)
```

```{r}
colnames(robo_maxmin) <- c("density", "tide", "top_bottom", "day", "temp_min", "temp_max")
colnames(do_diff_maxmin) <- c("tide", "treatment","day", "do_min", "do_max")

do_diff_maxmin$density <- str_extract(do_diff_maxmin$treatment, "^[^_]+")
do_diff_maxmin_2 <- do_diff_maxmin %>%
  filter(density %in% c("D", "S"))

do_diff_temp_maxmin <- left_join(robo_maxmin, do_diff_maxmin_2, by = c("day", "density", "tide"))
do_diff_temp_maxmin <- na.omit(do_diff_temp_maxmin)

do_diff_temp_maxmin$month <- month(do_diff_temp_maxmin$day)

```


## is DO min associated with intertidal heat stress 

Looks like bigger swing in DO diff when temperature is lower, so does less time emersed = more time immersed = smaller do minimum? 

Low tide def has more low points but not that many more, 

```{r}
do_diff_temp_maxmin %>%
  filter(top_bottom %in% c("0"))%>%
  ggplot(aes(x=temp_max, y = do_min, color = tide))+
  geom_point()+
  geom_smooth(method = "lm", se = TRUE,level = 0.95) +
  theme_classic()

model_data <- do_diff_temp_maxmin %>%
  filter(top_bottom %in% c("0", "2"))

model_DOtemp1 <-glmmTMB(do_min ~  density + temp_max + tide + month, data = model_data, family = gaussian()) #glmmTMB
summary(model_DOtemp1)
car::Anova(model_DOtemp1,type = "III")

model_DOtemp2 <-glmmTMB(do_min ~  density + temp_max * tide + month, data = model_data, family = gaussian()) #glmmTMB
summary(model_DOtemp2)
car::Anova(model_DOtemp2,type = "III")

model_DOtemp3 <-glmmTMB(do_min ~  density + temp_max * tide * month, data = model_data, family = gaussian()) #glmmTMB
summary(model_DOtemp3)
car::Anova(model_DOtemp3,type = "III")

model_DOtemp3 <-glmmTMB(do_min ~  density*tide + temp_max *month, data = model_data, family = gaussian()) #glmmTMB
summary(model_DOtemp3)
car::Anova(model_DOtemp3,type = "III")

#winning model
model_DOtemp3 <-glmmTMB(do_min ~  density+tide + temp_max *month, data = model_data, family = gaussian()) #glmmTMB
summary(model_DOtemp3)
car::Anova(model_DOtemp3,type = "III")



model_DOtemp4 <-glmmTMB(do_min ~  density * temp_max * tide * month, data = model_data, family = gaussian()) #glmmTMB
summary(model_DOtemp4)
car::Anova(model_DOtemp4,type = "III")

```
```{r}
model_DOtemp1 <-glmmTMB(do_min ~  density + temp_min + tide + month, data = model_data, family = gaussian()) #glmmTMB
summary(model_DOtemp1)
car::Anova(model_DOtemp1,type = "III")

model_DOtemp2 <-glmmTMB(do_min ~  density + temp_min * tide + month, data = model_data, family = gaussian()) #glmmTMB
summary(model_DOtemp2)
car::Anova(model_DOtemp2,type = "III")

#winning model
model_DOtemp3 <-glmmTMB(do_min ~  density + temp_min * tide * month, data = model_data, family = gaussian()) #glmmTMB
summary(model_DOtemp3)
car::Anova(model_DOtemp3,type = "III")

model_DOtemp4 <-glmmTMB(do_min ~  density * temp_min * tide * month, data = model_data, family = gaussian()) #glmmTMB
summary(model_DOtemp4)
car::Anova(model_DOtemp4,type = "III")
```
```{r}
model_DOtemp1 <-glmmTMB(do_min ~  density + temp_max + tide + month, data = do_diff_temp_maxmin, family = gaussian()) #glmmTMB
summary(model_DOtemp1)
car::Anova(model_DOtemp1,type = "III")

model_DOtemp2 <-glmmTMB(do_min ~  density + temp_max * tide + month, data = do_diff_temp_maxmin, family = gaussian()) #glmmTMB
summary(model_DOtemp2)
car::Anova(model_DOtemp2,type = "III")

#winning model
model_DOtemp3 <-glmmTMB(do_min ~  density + temp_max * tide * month, data = do_diff_temp_maxmin, family = gaussian()) #glmmTMB
summary(model_DOtemp3)
car::Anova(model_DOtemp3,type = "III")

model_DOtemp4 <-glmmTMB(do_min ~  density * temp_max* tide * month, data = do_diff_temp_maxmin, family = gaussian()) #glmmTMB
summary(model_DOtemp4)
car::Anova(model_DOtemp4,type = "III")
```




## is DO min associated with water temp
Seems like it might be a little bit, with little swings here and there especially for high tide, but yes higher water temp seems to go with greater do diff

```{r}
do_diff_temp_maxmin %>%
  filter(top_bottom %in% c("2", "0"))%>%
  filter(tide == "L")%>%
  ggplot(aes(x=temp_min, y = do_min, color = top_bottom))+
  geom_point()+
  theme_classic()
```

```{r}

```

